Название статьи

### 2015-10-23 common/packages.tex
- moved more stuff to "Common" (more work still needed to create reusable styles and templates) - added text about DOME
- added reviews for MetaLanguage, PSL/PSA - epic table with tools comparison
some editing of part 1
- font changed to 14pt to correspond to standard - moved part 5 and metalanguage to appendix to make core of the work smaller
Edited synopsis to syntactically comply with VAK requirements
Migrted to xetex compiler, used Times New Roman (as GOST 7.0.11 requires), used gost package and GOST 7.1-2003 formatting in bibliography, some formatting fixes

%%% Поля и разметка страницы %%%
\usepackage{lscape}		% Для включения альбомных страниц
\usepackage{geometry}	% Для последующего задания полей

%%% Кодировки и шрифты %%%
\usepackage{cmap}						% Улучшенный поиск русских слов в полученном pdf-файле
\usepackage[T2A]{fontenc}				% Поддержка русских букв
\usepackage[utf8]{inputenc}				% Кодировка utf8
\usepackage[english, russian]{babel}	% Языки: русский, английский
%\usepackage{pscyr}						% Красивые русские шрифты

@@

%%% Гиперссылки %%%
\usepackage[linktocpage=true,plainpages=false,pdfpagelabels=false]{hyperref}

@@

% Для форматирования заголовков
\usepackage{sectsty}

@@

>>>>

%%% Поля и разметка страницы %%%
\usepackage{lscape}							% Для включения альбомных страниц
\usepackage{geometry}						% Для последующего задания полей
\usepackage[strict]{changepage}				% Для управления размерами полей страницы

%%% Шрифты и локализация %%%
\usepackage{polyglossia}
\setdefaultlanguage[babelshorthands=true]{russian}

\usepackage{fontspec}
\setmainfont{Times New Roman}
\newfontfamily{\russianfonttt}{Times New Roman}

@@

%%% Гиперссылки %%%
\usepackage[xetex,linktocpage=true,plainpages=false,pdfpagelabels=false]{hyperref}

@@

% Для центрирования заголовков. Пакет sectsty не работает с пакетом extsizes, поэтому здесь не используется.
\usepackage[center]{titlesec}

@@

% Список сокращений
\usepackage{etoolbox}
\usepackage[footnote]{acronym}

% Несколько библиографий (например, ВАКовские и другие работы)
\usepackage{multibib}
